Matching bullets

### 2015-11-16 imaging-paper.Rnw
personal highlighter
typo
couple of comments

%---------------------------------------------------
\usepackage[cmex10]{amsmath}
\usepackage{amssymb}
\usepackage{color}
% \usepackage[dvipsnames,svgnames]{xcolor}
% \usepackage{ulem}
% \usepackage[section]{placeins}
\usepackage[caption=false,font=footnotesize,labelfont=sf,textfont=sf]{subfig}
% \usepackage{sidecap}
\usepackage{multirow}
\usepackage{bbm}
\usepackage{url}
\usepackage{xr}
\usepackage{xr-hyper}
\usepackage{afterpage}

@@

In the Hamby Study, x3p files were created using a NanoFocus lens at 20x resolution. \hh{not sure where this sentences best goes.}

@@

It's clear that our next approach must be to model the signal in order to focus on the noise, given that the noise should correspond to bullet markings.

>>>>

%---------------------------------------------------
\usepackage[cmex10]{amsmath}
\usepackage{amssymb}
\usepackage{color}

\newcommand{\hh}[1]{{\color{magenta} #1}}
% \usepackage[dvipsnames,svgnames]{xcolor}
% \usepackage{ulem}
% \usepackage[section]{placeins}
\usepackage[caption=false,font=footnotesize,labelfont=sf,textfont=sf]{subfig}
% \usepackage{sidecap}
\usepackage{multirow}
\usepackage{bbm}
\usepackage{url}
\usepackage{xr}
\usepackage{xr-hyper}
\usepackage{afterpage}

@@

In the Hamby Study, x3p files were created using a NanoFocus lens at 20x magnification. \hh{not sure where this sentences best goes.}

@@

It's clear that our next approach must be to model the signal in order to focus on the noise, given that the noise should correspond to bullet markings.
\hh{XXX let's not call the markings noise - that has the conotation of them being random. The markings are also a signal, it is just dominated by the stronger signal of the land structure. We often go through a process of multiple steps to get close to the more interesting, smaller signal. }
\hh{XXX on a side note - I've got a different relative path to the x3p bullet files ... should we assume a data directory inside the folder? Then we don't have to push the files on a github repo again, but are using the same file structure?}
